---
title: "simulation-v4"
output:
  rmarkdown::html_document: default
  rmarkdown::html_vignette: default
vignette: |
  %\VignetteIndexEntry{simulation-v2} 
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

<style>
    body .main-container {
        max-width: 2000px;
    }
</style>

```{r, message=FALSE, warning=FALSE}
library(dplyr)
library(ggplot2)
devtools::load_all()
load("../simulation/simu_qte_v4.Rdata")
```

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width=14,
  fig.height=14
)
```

# Simulation Setup 

We conducted simulation studies to verify the validity of the proposed IPW and AIPW estimators. 

Simulation set up 

- Total sample size: `n = 400`
- Analysis time $L = 1$
- Covariates $X$ is generated from $\mathcal{N}(0.5, 1)$
- Treatment group $A$ is generated from $Bernoulli(p)$, where $p=logit^{-1}(-0.25 + 0.5 * x)$ such that the randomization ratio is close to 1:1. 
- Outcome $Y$ is generated from $\mathcal{N}(\eta, 1)$, where $\eta =  0.4 + 0.8 * A + 0.3 * X$.
- Death time: $T \sim \exp(\lambda)$, where $\lambda = exp(-2 + 0.5 * X)$ (for a simple Cox PH model)
- Censoring time: $C \sim \exp(-2 + 0.4 * x)$
- Observed time: $U = T \wedge C$
- Event indicator: $\delta = T < C$

- Missing data: `y_obs` in simulated data
  - $Y$ is missing if $U < L$
  - we summarize the missing data proportion based on the event indicator. 
- Actual data: the underline true value of `y_actual` in simulated data 
  - `y_actual` = $\min(y) - 1$ if $T < L$    

## Example of simulated data

```{r, message = FALSE}
head(db) %>% select(a, x, y, y_obs, y_actual, event_time, censor_time, obs_time, status, analysis_time) %>% 
             knitr::kable(digits = 3)
```
## Method to calculate true value 

The true value is estimated by `y_actual` without using propensity score and censoring adjustment. 

The sample size to calculate true value is 10,000 with replication of 1,000 times.

We calculate the true value for different `xi` from 0.35 to 0.95. 

```{r}
est0 %>% knitr::kable(digits = 2)
```

## Model Estimation

The calculation is within each treatment group

1. Propensity score: Fit a logistic model: `glm(a ~ x, family = "binomial", data = db)`
1. IPW weight $\pi$: Coxph model: `coxph(Surv(obs_time, 1 - status) ~ x, data = db)` and calculate the probability at the minimal of `obs_time` and `analysis_time`
1. $F(y\mid x; \theta)$
  - Fit a linear model based on observed outcome `lm(y_obs ~ x, data = db)`
  - Calculate the scaled CDF for `f_q`
  
```{r, eval = FALSE}
y_std <- (q - db$y_mean) / db$y_sigma
rho + (1 - rho) * pnorm(y_std)
```

1. $R$: `(obs_time > analysis_time) | (obs_time <= analysis_time & status = TRUE)`

## Simulation Setup

- `a`: treatment group
- `xi` the quantile of interest 
- `n`: sample size in each group for true value estimation
- `pct_missing`: Percent of subject with missing value at analysis time $L$
- `pct_missing_death`: Percent of subject dead on or before analysis time $L$
- `pct_missing_censor`: Percent of subject censored on or before analysis time $L$

For the IPW part, we considered two types:

- Type 1: same as in formula (5) of the manuscript 
- Type 2: we calculate the equation based on the formula below. That only use observed data.  

$$\sum \{ I(Y < q) -  \tilde{F}_a(y \mid X)) \} / e(X_i; \alpha)$$

## Missing data and censoring proportion 

```{r}
meta %>% select(a, n, starts_with("pct")) %>% unique()
```

## Simulation Results

- `xi` the quantile of interest 
- `use_propensity`: whether to use propensity score is the estimator equation.
- `use_km`: whether to use KM estimator to adjust censoring 
- `km_rho`: method to estimate the probability of death at $L$
  + `rho`: raw estimator (observed death before $L$) / number of subjects
  + `rho_km`: estimated from Cox model `coxph(Surv(obs_time, 1 - status) ~ x, data = db)` at time $L$.
  + `rho_km_simple`: estimated from KM estimator at time $L$.
- `type`: using `IPW` (formula 5) or `AIPW` (formula 6).
- `x0`, `x0_true`: estimated or true value for the percentile in control group
- `x1`, `x1_true`: estimated or true value for the percentile in treatment group
- `diff`, `diff_true`: estimated or true value for the percentile difference between two group

### Results with observing censoring

All proposed methods performs well under true value. Here we display the results when `xi = 0.5`. 
```{r}
est1 %>% ungroup() %>% subset(xi == 0.5 & km_rho == "rho_km") %>%
  mutate_if(is.numeric, round, 3)  %>% show_db()
```
For the results with different `xi`, we summarize the results in figures below
```{r, echo = FALSE}
s1
```
## Robustness of the estimator 

### Case 1: incorrect outcome regression 

We consider a situation when the outcome regression is not correct. 

The outcome data $Y$ is simulated from `y <- rnorm(n, 0.4 + 0.8 * a + 0.3 * x + x * x2, sd = 1)`, where $X_2 \sim \mathcal{N}(0, 1)$. Everything else are the same. 

```{r, echo = FALSE}
s4
```

### Case 2: incorrect propensity score

We consider a situation when the propensity score model is not correct. 

The treatment group is simulated from `prob <- inv_logit(-0.25 + 0.5 * x + x * x2)`, where $X_2 \sim \mathcal{N}(0, 1)$. Everything else are the same. 

```{r, echo = FALSE}
s3
```
