---
title: "simulation-v7"
output:
  rmarkdown::html_document: default
  rmarkdown::html_vignette: default
vignette: |
  %\VignetteIndexEntry{simulation-v2} 
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

<style>
    body .main-container {
        max-width: 2000px;
    }
</style>

```{r, message=FALSE, warning=FALSE}
library(dplyr)
library(ggplot2)
devtools::load_all()
load("../simulation/simu_qte_v7.Rdata")
```

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width=14,
  fig.height=14
)
```

# Additional Simulation Results for Difference Censoring Proportion

We further evaluate the performance of the proposed method under different censoring proportion. All set up are the same as in simultion_v5.Rmd report except 
the intercept of the censoring distribution. 

## Missing data and censoring proportion 

```{r}
result_meta %>% subset(scenario != 4) %>% mutate_if(is.numeric, round, digits = 1) %>% show_db()
```


## S1

- S1: Censoring time: $C \sim \exp(-2 + 0.8 * x)$

```{r, echo = FALSE}
s1
```

## S2

- S2: Censoring time: $C \sim \exp(-2 + 1 * x)$

```{r, echo = FALSE}
s2
```

## S3

- S3: Censoring time: $C \sim \exp(-2 + 2 * x)$

```{r, echo = FALSE}
s3
```

## S4

- S4: Censoring time: $C \sim \exp(-2 + 3 * x)$

```{r, echo = FALSE}
s4
```
